% This is the ninth iteration of my resume.

\documentclass[letterpaper, 10 pt]{article}
\usepackage[left=0.60 in, right=0.60 in, top=0.60 in, bottom=0.60 in]{geometry}
\pagestyle{empty}
\usepackage{fontspec}
\setmainfont{Times New Roman}
%%\setmainfont{Cambria}
%%\setmainfont{Garamond}
%%\setmainfont{Arial}

\linespread{1.00} % 'linespread' command used to change the 'baselineskip' without changing the font size.

\usepackage{titlesec}
% Will use only subsubsections for the different parts of this resume.
\titlespacing*\subsection{0pt}{0.40 \baselineskip}{0.15 \baselineskip} %% Spacing for subsection headings.
\titlespacing*\subsubsection{0pt}{0.20 \baselineskip}{0.15 \baselineskip} %% Spacing for subsubsection headings.
 
\begin{document}
% Personal Information
\centerline{\huge Jos\'e Bravo \hfill \normalsize 5440 Bonniemae Way, Sacramento, CA 95820 | 831.214.1780}
\hspace*{\fill} joepbravo@gmail.com | GitHub: jbravo87

%%\noindent\rule[0.10 ex]{\linewidth}{1.75 pt}

% Can alternate between work history or education first to suit needs.
% Generally, can switch subsubsections to fit needs.
\subsection*{Education}
%%\rule[0.75ex]{\linewidth}{0.4pt}
\noindent\rule[0.75ex]{\linewidth}{0.55 pt}
Bachelor of Arts, \textit{Applied Mathematics} \\
Bachelor of Arts, \textit{Physics}

% Need this space for proper indentation.
California State University, Sacramento | Sacramento, CA | May 2021 % Finished the program in May, but awarded the degree in June?
\subsubsection*{Relevant Coursework}
\quad Classical Mechanics, Optics, Thermodynamics, Electronics and Instrumentation, Advanced Physics Laboratory, Biology I, General Chemistry I \& II, Ordinary Differential Equations, Mathematical Methods, Real Analysis, Complex Analysis, Abstract Algebra, Programming Methods, Probability and Statistics, Statistical Computing, Big Data % Chose not to use bullet points to conserve space.

\subsubsection*{Laboratory Skills}
\quad Chemistry: practiced titration, spectroscopy, reflux, distillation, and acid-base interactions. Electronics: built linear and non-linear circuits, used sensors and transducers, built operational amplifiers, learned basic digital circuitry, and introduced to computerized data acquisition. Optics: studied geometrical optics, single and double slit interference and diffraction, polarization, error analysis, and used Michelson interferometers, He-Ne lasers, and photomultipliers.

\subsubsection*{Projects}
\centerline{\textit{Final Project – STAT 196K Big Data} \hfill May 2021}
\begin{itemize}
\setlength\itemsep{0.10 em}
\item Statistical analysis of simulated data from the ATLAS particle physics experiment made available through CERN Open Source. With over 10 GB of zip CSV data, each file its own collision event, wanted to study the decay of Z bosons to positrons. The objective was to determine a relationship between displacement/location in the collider and the energy of the subatomic particle using K-means clustering. Used AWS as my cloud platform and Julia programming.
\end{itemize}
\centerline{\textit{Topological Flips – Senior Project} \hfill Summer 2020 – May 2021}
\begin{itemize}
\setlength\itemsep{0.10 em}
\item Studied Lie Groups to describe skateboard stunts as algebraic structures. Our group produced a theorem to describe skateboard tricks from four fundamental stunts/elements in $SO(3)$.
\item Used SymPy to create a catalog of stunts using symbolic matrices. Then created Python software to allow users to view rotational matrix or render a GIF of a stunt.
\end{itemize}
%NLP or natural language processing.
\subsection*{Technical Profile}
\noindent\rule[0.75ex]{\linewidth}{0.55 pt}
\begin{itemize}
\setlength\itemsep{0.10 em}
\item Programming proficiency with Python (Spyder), R (RStudio), and Julia (Juno). Capable with Java (BlueJ), C++, and SQL. Software literacy include Wolfram Mathematica,\,\LaTeX, Bash (Unix shell), Git version control, HTML, XML, Markdown, MS Office Suite. Studied principles of OOP by building, iterating, validating, and troubleshooting/debugging algorithms and models. Also versed in functional programming.
\item Experience with statistical modeling, principles, techniques, and applications complemented by knowledge of major statistical software. For given data, implemented distributional tests, unsupervised learning methods such as K-means for clustering or principal components analysis (PCA), or supervised learning such as linear regression or generalized additive models (GAMs).
\item Knowledge of big data analytics via training in cloud computing. Created S3 buckets, configured AWS Cloudformation using a JSON template, and run query in Amazon Athena using standard SQL. Used a publicly available COVID-19 data lake. Also used AMI and EC2 instances from AWS to manipulate large data sets for exploratory data analysis.
\item Extensive use of libraries such as Plots and Plotly in Julia, Matplotlib and Plotly in Python, and ggplot2 in R for data visualization and plotting. Built dashboards using Shiny in RStudio.
\item Practiced reservoir sampling, pipeline implementation, and natural language processing. Worked with dense and sparse data structures and learned dimensional reduction. Optimized memory efficiency by monitoring performance, identifying bottlenecks, and utilizing parallel processing or multiprocessing when necessary.
\item Technical writing and public speaking skills as well as a high level of interpersonal skills. Languages: Spanish (Read/Speak)
\end{itemize}

\subsection*{Employment History}
\noindent\rule[0.75ex]{\linewidth}{0.55 pt}
%%\rule[0.75ex]{\linewidth}{0.4pt}

\noindent
\centerline{Monterey Bay Aquarium Gift and Bookstore - Monterey, CA \hfill May 2012 – June 2018}

Sales, Stock, \& Warehouse Associate
%%Sales/Stock/Warehouse Associate \\
%%\centerline{National Union of Healthcare Workers - San Francisco, CA \hfill January 2009 – August 2010}

%%Organizer \\
%%\centerline{SEIU United Healthcare Workers - West - Sacramento, CA \hfill October 2007 – January 2009}

%%External Organizer  \\
%%\centerline{UA Plumbers \& Steamfitters Local 159 / UC Berkeley Labor Center - Martinez/Berkeley, CA \hfill June 2007 – August 2007}

%%Organizer - Intern / Labor Summer Internship \\
\end{document}

% End of "JBravo_Edition9".
